Abstract

### 2025-05-22 output/Letter_to_editor_reviewers.Rmd
Add verbatim of reference to datasets in paper

The datasets we use in our paper are examples of item parameter estimates, taken from the literature.
As they only serve exemplification purposes and are not the main focus of our article, we deem it more appropriate to describe their details in the corresponding section of the manuscript.
We have added a short reference to them in the introduction, to make sure their pertinence as examples is clear.

<!-- TODO: Include text added -->

>>>>

The datasets we use in our paper are examples of item parameter estimates, taken from the literature.
As they only serve exemplification purposes and are not the main focus of our article, we deem it more appropriate to describe their details in the corresponding section of the manuscript.
We have added a short reference to them in the last paragraph of our introduction (p. <!-- TODO: Complete -->, lines <!-- TODO: Complete -->), to make sure their pertinence as examples is clear.

> These examples, from the cognitive and the non-cognitive domain, respectively,
are taken from the MIRT literature:
One of them is a classic dataset, often used to exemplify
the use of the `r MODEL_ACRONYM` model [@reckase_multidimensional_2009];
the other one, an application in marketing research [@tezza_modelo_2018].
